---
title: "{{{name}}}"
date: today
params:
  name: "{{{name}}}"
---

**Updated: `r format(Sys.time(), '%Y-%m-%d %H:%M:%S', tz = 'CET')` CET.**

```{r}
#| label: params
#| eval: !expr interactive()
#| include: false
params <- list(name = "{{{name}}}")
```

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false
wd <- "{{{path_proj}}}"
if (basename(getwd()) != wd) {
  setwd(here::here(wd))
}
here::i_am(paste0(params$name, ".qmd"), uuid = "{{{uuid}}}")
qproj::proj_create_dir_target(params$name, clean = FALSE)

# convenience helpers
path_target <- qproj::proj_path_target(params$name)
path_source <- qproj::proj_path_source(params$name)
path_raw <- path_source("00-raw")
path_resource <- here::here(path_raw, "d00-resource")
path_data <- here::here(path_raw, paste0("d", params$name))
dir.create(path_raw, recursive = TRUE, showWarnings = FALSE)
dir.create(path_data, recursive = TRUE, showWarnings = FALSE)
dir.create(path_resource, recursive = TRUE, showWarnings = FALSE)
```

```{r}
#| label: packages
#| message: false
#| warning: false
suppressPackageStartupMessages({
  library(here)
  library(conflicted)
  library(tidyverse)
  library(data.table)
  devtools::load_all()
})
```

## Workflow tips

- Write results to your own directory: `path_target("my-file.csv")`.
- Read earlier outputs (only those that run before this file): `path_source("00-import", "raw.csv")`.
- Keep each file responsible for its own data directory to avoid accidental overwrites.

## Tasks

This section is designated for your workflow implementation. **Please write all your analysis and processing code here.**

Maintaining your code within this section ensures a clean project structure and facilitates reproducibility. We recommend organizing your workflow into modular tasks—such as data cleaning, analysis, and visualization—using distinct code chunks.

::: {.callout-note}
## Example structure

This is an example structure to get you started. You can modify it as per your needs.
:::

### Task 1: Data import

```{r}
#| label: data-import
#| cache: true

# Your data import code here
```

## Files written

These files have been written to the target directory, `r paste0("data/", params$name)`:

```{r}
#| label: list-files-target
knitr::kable(qproj::proj_dir_info(path_target(), tz = "CET"))
```
